\documentclass[crop=false,a4paper,oneside,11pt]{standalone}
\usepackage{a4wide,graphicx,fancyhdr,amsmath,amssymb,float,graphicx,color,geometry,xcolor,titlesec,colortbl,tabu,color}
\usepackage[parfill]{parskip}
\usepackage[nodayofweek]{datetime}
\usepackage{listings}
%----------------------- Macros and Definitions --------------------------

%fast change of things
\newcommand{\mysubject}{2IO70 DBL Embedded Systems}
\newcommand{\myassignment}{Group 12}

%\definecolor{titlepagecolor}{cmyk}{1,.60,0,.40}
%\definecolor{namecolor}{cmyk}{1,.50,0,.10}


\setlength\headheight{20pt}
\addtolength\topmargin{-10pt}
\addtolength\footskip{20pt}

% Define light and dark Microsoft blue colours
\definecolor{MSBlue}{rgb}{.204,.353,.541}
\definecolor{MSLightBlue}{rgb}{.31,.506,.741}
\arrayrulecolor{MSLightBlue}

% Set formats for each heading level

\titleformat*{\section}{\Large\bfseries\sffamily\color{MSBlue}}
\titleformat*{\subsection}{\large\bfseries\sffamily\color{MSLightBlue}}

%date format
\newdateformat{mydate}{\monthname[\THEMONTH] \THEYEAR}

\fancypagestyle{plain}{%
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot[CO] {\thepage}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}


%--------------------------------- Text ----------------------------------
\setcounter{secnumdepth}{0}
\begin{document}

\section{References}
$[1]$ A. Wolff. \emph{Automated Label Placement in Theory and Practice}. PhD thesis Freie Univeristät Berlin, May 1999. Section 3.2.

$[2]$ J. Christensen, J. Marks and S. Shieber. An Empirical Study of Algorithms for Point-Feature Label Placement. In \emph{ACM Transactions on Graphics}, Volume 14, Issue 3, pages 203-232 July 1995.

$[3]$ A. Wolff. \emph{The Map-Labeling Bibliography}. URL: http://i11www.iti.uni-karlsruhe.de/~awolff/map-labeling/bibliography/, accessed April 27th 2015.

$[4]$ E. Imhof. Positioning Names on Maps. In \emph{The American Cartographer}, Volume 2, Issue 2, pages 128-144, 1975.

$[5]$ A. Cook and C. Jones. A Prolog Rule-Based System for Cartographic Name Placement. In \emph{Computer Graphics Forum}, Volume 9, Issue 2, pages 109-126, 1990.

$[6]$ G. Raidl. A Genetic Algorithm for Labeling Point Features. In \emph{Proc. The International Conference on Imaging Science, Systems, and Technology}. Pages 189-196, 1998.

$[7]$ K. Mote. Fast Point-Feature Label Placement for Dynamic Visualizations. In \emph{Information Visualization}. Volume 6, Issue 4, pages 249-260, December 2007.

$[8]$ K. Been, E. Daiches and C. Yap. Dynamic Map Labeling. In \emph{Proc. IEEE Transactions on Visualization and Computer Graphics}. Volume 12, Issue 5, pages 773-780, September 2006.
\end{document}
